---
title: "AY 2019---Turning of the Tide?"
author: "Kurtis Pivert, **ASN Data Science Officer**"
date: "August 2018"
output:
  powerpoint_presentation
---

```{r setup, include=FALSE}

require(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
require(extrafont)
require(rmarkdown)
loadfonts(quiet = TRUE)
require(ggrepel)
require(RColorBrewer)
require(pander)
require(tidyverse)
  
```



```{r Load Data, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}

  ## Edu Status
  eras <- read_excel(here::here("01_data", 
                                "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"), 
                     sheet = "By Edu Status")

  eras <- eras %>% mutate(month = lubridate::month(month_year))
  
  ## Historical Totals
  eras_hist <- read_excel(here::here("01_data", 
                                     "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"), 
                          sheet = "Historical Totals")

  eras_hist <- eras_hist %>% mutate(month = lubridate::month(`Month/Year`))
  
  
```


# Total candidates in July are up ...


```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  eras_colors <- c("2014" = "#cccccc", "2015" = "#cccccc",  "2016" = "#cccccc", 
                    "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#3366cc")
  
  eras_hist %>% filter(month == 7) %>% 
    ggplot(aes(x = `ERAS Year`, y = `# of Applicants`)) +
    #geom_line(color = "#cc3366", lwd = 1.5) +
    geom_bar(stat = "identity", fill = c("#cccccc", "#cccccc", "#cccccc", 
                                         "#cccccc", "#cccccc","#3366cc"),
             width = .7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
    ylab("No. of Candidates") +
    xlab("ERAS Year") +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    labs(title = "Total Nephrology Candidates in July by ERAS Year",
         caption = "Source: ERAS, 2014\u20132018")
  
```


# ... and candidate trends are reversing.

Starting with last year's application cycle, the year-over-year trend of declining 

```{r Figure 2, echo=FALSE,  message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  eras_hist %>% filter(month == 7) %>% mutate(lagged = lag(`# of Applicants`)) %>% 
    mutate(Pct_Change = ((`# of Applicants` - lagged) / lagged)) %>% 
    filter(`ERAS Year` != 2014) %>% 
    ggplot(aes(x = `ERAS Year`, y = Pct_Change, fill = sign(Pct_Change))) +
    geom_bar(stat = "identity", width = .7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
  labs(y = "% Change Candidates",
      x = "ERAS Year") +
    theme(legend.position = "none") +
    geom_text(aes(label = scales::percent(Pct_Change), 
                  y = (Pct_Change + 0.007 * sign(Pct_Change))), family = "Roboto") +
    scale_y_continuous(labels = scales::percent) +
    labs(title = "Percent Change Year over Year\u2014Candidates in July",
            caption = "Source: ERAS, 2014\u20132018")
   
```


# Applications to nephrology fellowships are up slightly ...   


```{r Figure 3, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  eras_hist %>% filter(month == 7) %>% 
    ggplot(aes(x = `ERAS Year`, y = `# of Applications`)) +
    geom_bar(stat = 'identity', fill = c("#cccccc", "#cccccc", "#cccccc", 
                                         "#cccccc", "#cccccc","#3366cc"),
             width = 0.7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    labs(
      y = "No. of Applications",
      x = "ERAS Year") +
    labs(title = "Total Nephrology Applications in July by ERAS Year",
         caption = "Source: ERAS, 2014\u20132018")

  
```


# ... and growing slowly year over year.


```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  eras_hist %>% filter(month == 7) %>% mutate(lagged = lag(`# of Applications`)) %>% 
    mutate(Pct_Change = ((`# of Applications` - lagged) / lagged)) %>% 
    filter(`ERAS Year` != 2014) %>% 
    ggplot(aes(x = `ERAS Year`, y = Pct_Change, fill = sign(Pct_Change))) +
    geom_bar(stat = "identity", width = .7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(family = "Roboto Medium", hjust = 0.5),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
    ylab("% Change Applications") +
    theme(legend.position = "none") +
    geom_text(aes(label = scales::percent(Pct_Change), 
                  y = (Pct_Change + 0.007 * sign(Pct_Change))), family = "Roboto") +
    scale_y_continuous(labels = scales::percent) +
    labs(title = "Percent Change Year over Year\u2014Applications in July",
         caption = "Source: ERAS, 2014\u20132018")
   
```


# IMG candidates are back ...


```{r Figure 5, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  
        eras <-  eras %>% mutate(Label = paste0(edu_status, " ", 
                                                as.character(num_candidate)))  
        
        eras %>% filter(month == 7) %>% ggplot() +
          geom_line(aes(x = as.factor(ERAS), y = num_candidate, group = edu_status, 
                                      color = edu_status), lwd = 1.2) + 
          geom_point(aes(x = as.factor(ERAS), y = num_candidate, color = edu_status), 
                     size = 2) +
          theme_minimal(base_size = 14, base_family = "Roboto") +
          scale_color_brewer(palette = "Set1") +
          xlab("") +
          ylab("No. of Candidates") +
          geom_text(data = subset(eras, ERAS == 2018 & month == 7), 
                    aes(x = as.factor(ERAS), y = num_candidate, color = edu_status, 
                        label = Label), 
                          size = 4, hjust = 1.1, family = "Roboto") +
          geom_text(data = subset(eras, ERAS == 2019 & month == 7), 
                    aes(x = as.factor(ERAS), y = num_candidate, color = edu_status, 
                        label = Label), 
                          size = 4, hjust = -.15, family = "Roboto")+
          theme(legend.position = "none", axis.text = element_text(family = "Roboto"),
                panel.background = element_rect(fill = "#fffff3", 
                                                color = "#fffff3"),
                plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
                plot.title = element_text(family = "Roboto Medium", hjust = 0.5)) +
          labs(title = "July AY 2019 Candidates by Educational Status",
               caption = "Source: ERAS, 2014\u20132018") 
          
        
        
```


# ...but total candidates ...   


```{r Figure 6, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  eras_colors <- c("2014" = "#cccccc", "2015" = "#cccccc",  "2016" = "#cccccc", 
                    "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#3366cc") 
  
  Avg <- eras_hist %>% filter(!`ERAS Year` == 2019) %>% group_by(`ERAS Year`) %>% 
  summarize(Total = sum(`# of Applicants`)) %>% summarize(Avg = mean(Total))
               

  eras_hist %>% group_by(`ERAS Year`) %>% 
    summarise(Total = sum(`# of Applicants`)) %>% 
    ggplot(aes(x = `ERAS Year`, y = Total)) +
    geom_bar(stat = "identity", fill = c("#cccccc", "#cccccc", "#cccccc", 
                                         "#cccccc", "#cccccc","#3366cc"),
             width = 0.7) +
    theme_minimal(base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust =0.5, family = "Roboto Medium")) +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    #geom_hline(aes(yintercept = mean(Total))) + 
    geom_hline(aes(yintercept = Avg$Avg)) + 
    theme(legend.position = "none") +
    geom_text(aes(label = "Mean Total Candidates", x = 2018.5, y = 500),
              family = "Roboto", color = "#3366cc") +
    ylab("Total Candidates per Application Cycle") +
    labs(title = "Total Candidates by ERAS Year (AY 2019 = July Only)",
         caption = "Source: ERAS, 2014\u20132018")
 

```


# ...and applications are still down compared to historic averages. 


```{r Figure 7, echo=FALSE,  message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  eras_colors <- c("2014" = "#cccccc", "2015" = "#cccccc",  "2016" = "#cccccc", 
                    "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#3366cc") 
                 
  Avg_Apps <- eras_hist %>% filter(!`ERAS Year` == 2019) %>% group_by(`ERAS Year`) %>% 
  summarize(Total = sum(`# of Applications`)) %>% summarize(Avg = mean(Total))                   

  eras_hist %>% group_by(`ERAS Year`) %>% 
    summarise(Total = sum(`# of Applications`)) %>% 
    ggplot(aes(x = `ERAS Year`, y = Total)) +
    geom_bar(stat = "identity", 
             fill = c("#cccccc", "#cccccc", "#cccccc", "#cccccc", "#cccccc",
                                 "#3366cc"),
             width = 0.7) +
    theme_minimal(base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium")) +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    geom_hline(aes(yintercept = Avg_Apps$Avg)) + 
    theme(legend.position = "none") +
    geom_text(aes(label = "Mean Total Applications", x = 2018.5, y = 9900),
              family = "Roboto", color = "#3366cc") +
    ylab("Total Applications per Application Cycle") +
    labs(title = "Total Applications by ERAS Year (AY 2019 = July Only)",
         caption = "Source: ERAS, 2014\u20132018")
 

```


# Up Next

Future _Data Briefs_ will report ERAS application data as it becomes available. 

_**Questions? Comments?**_ 

Contact ASN Data Science Officer Kurtis Pivert
at 202-699-0238 or [kpivert@asn-online.org](mailto:kpivert@asn-online.org).

