---
title: "August/September ERAS Applications"
author: "Kurtis Pivert, **ASN Data Science Officer**"
date: "October 2018"
output:
  powerpoint_presentation
---

```{r Load Packages , message=FALSE, warning=FALSE, include=FALSE}

require(knitr)
require(readxl)
require(tidyverse)
require(extrafont)
require(rmarkdown)
loadfonts(quiet = TRUE)
require(ggrepel)
  
```


```{r Load Data, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}

## Edu Status

eras <- read_excel(
  here::here(
    "01_data", "2018-10-02_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"
    ), 
  sheet = "By Edu Status"
  )

eras <- eras %>% 
  mutate(
    month = lubridate::month(month_year)
  )
  
## Historical Totals
eras_hist <- read_excel(
  here::here(
    "01_data", "2018-10-02_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"
    ), 
  sheet = "Historical Totals"
  )

eras_hist <- eras_hist %>% 
  mutate(
    month = lubridate::month(`Month/Year`)
  )
  
  
```


# AY 2019 Nephrology Match Update: August/September ERAS Applications

# Fall Rebound in Candidates---August  

```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}

eras_colors <- c(
  "2014" = "#cccccc", "2015" = "#cccccc", "2016" = "#cccccc", 
  "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#4267b1"
)

## August_1
eras_hist %>% 
  filter(month == 8) %>% 
  ggplot(
    aes(x = `ERAS Year`, y = `# of Applicants`)
  ) +
  geom_bar(
    stat = "identity", 
    width = .7, 
    fill = c(
      "#cccccc", "#cccccc", "#cccccc",  "#cccccc", "#cccccc","#4267b1"
    )
  ) +
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
  ) +
  theme(
    panel.grid.minor = element_blank(), 
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3")
  ) +
  scale_x_continuous(
    breaks = 2014:2019, 
    labels = as.character(2014:2019)
  ) +
  labs(title = "Total Nephrology Candidates in August by ERAS Year", 
       y = "No. of Candidates",
       x = "ERAS Year",
       caption = "Source: ERAS, 2014\u20132018")

```

# Fall Rebound in Candidates---September

```{r Figure 2, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
## September
eras_hist %>% 
  filter(month == 9) %>% 
  ggplot(
    aes(x = `ERAS Year`, y = `# of Applicants`)
  ) +
  geom_bar(
    stat = "identity", 
    width = .7, 
    fill = c(
      "#cccccc", "#cccccc", "#cccccc",  "#cccccc", "#cccccc","#4267b1"
    )
  ) +
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
  ) +
  theme(
    panel.grid.minor = element_blank(), 
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3")
  ) +
  scale_x_continuous(
    breaks = 2014:2019, 
    labels = as.character(2014:2019)
  ) +
  labs(title = "Total Nephrology Candidates in September by ERAS Year", 
       y = "No. of Candidates",
       x = "ERAS Year",
       caption = "Source: ERAS, 2014\u20132018")

```

# ...and Applications---August 

```{r Figure 3, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, dpi= 300}

## August_2 
eras_hist %>% 
  filter(month == 8) %>% 
  ggplot(aes(x = `ERAS Year`, y = `# of Applications`)) +
  geom_bar(
    stat = 'identity', 
    fill = c("#cccccc", "#cccccc", "#cccccc","#cccccc", "#cccccc","#4267b1"), 
    width = 0.7
  ) + 
  theme_minimal(base_size = 14, base_family = "Roboto") + 
  theme(
    panel.grid.minor = element_blank(), 
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"
    ), 
    plot.title = element_text(
      hjust = 0.5, 
      family = "Roboto Medium"
    ),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"
    )
  ) +
  scale_x_continuous(
    breaks = 2014:2019, 
    labels = as.character(2014:2019)
  ) + 
  labs(title = "Total Nephrology Applications in August by ERAS Year", 
       caption = "Source: ERAS, 2014\u20132018",
       y ="No. of Applications",
       x = "ERAS Year")

```

# ...and Applications---September 

```{r Figure 4, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, dpi= 300}
## September_2 
eras_hist %>% 
  filter(month == 9) %>% 
  ggplot(aes(x = `ERAS Year`, y = `# of Applications`)) +
  geom_bar(
    stat = 'identity', 
    fill = c("#cccccc", "#cccccc", "#cccccc","#cccccc", "#cccccc","#4267b1"), 
    width = 0.7
  ) + 
  theme_minimal(base_size = 14, base_family = "Roboto") + 
  theme(
    panel.grid.minor = element_blank(), 
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"
    ), 
    plot.title = element_text(
      hjust = 0.5, 
      family = "Roboto Medium"
    ),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"
    )
  ) +
  scale_x_continuous(
    breaks = 2014:2019, 
    labels = as.character(2014:2019)
  ) + 
  labs(title = "Total Nephrology Applications in September by ERAS Year", 
       caption = "Source: ERAS, 2014\u20132018",
       y ="No. of Applications",
       x = "ERAS Year")


```


# Educational Status---August
 

```{r Figure 5, echo=FALSE,  message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  
eras <-  eras %>% 
  mutate(
    Label = paste0(edu_status, " ",
                   as.character(num_candidate))
  )  

 ## August_3
eras %>% 
  filter(month == 8) %>% 
  ggplot() +
  geom_line(
    aes(x = as.factor(ERAS), 
        y = num_candidate, 
        group = edu_status, 
        color = edu_status), 
    lwd = 1.2) + 
  geom_point(
    aes(x = as.factor(ERAS), 
        y = num_candidate, 
        color = edu_status), 
    size = 2) +
  theme_minimal(base_size = 14, base_family = "Roboto") +
  scale_color_brewer(palette = "Set1") +
  xlab("") +
  ylab("No. of Candidates") +
  geom_text(
    data = subset(eras, ERAS == 2018 & month == 8), 
    aes(
      x = as.factor(ERAS), 
      y = num_candidate, 
      color = edu_status, 
      label = Label
    ), 
    size = 4, 
    hjust = 1.1, 
    family = "Roboto"
  ) +
  geom_text(
    data = subset(eras, ERAS == 2019 & month == 8),
    aes(
      x = as.factor(ERAS),
      y = num_candidate, 
      color = edu_status,
      label = Label),
    size = 4, 
    hjust = -.15, 
    family = "Roboto"
  ) +
  theme(
    legend.position = "none", 
    axis.text = element_text(family = "Roboto"),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(family = "Roboto Medium", hjust = 0.5)
  ) +
  labs(
    title = "August Candidates by Educational Status \nAY 2018 and AY 2019", 
    caption = "Source: ERAS, 2014\u20132018") 

```

# Educational Status---September
 

```{r Figure 6, echo=FALSE,  message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}

## September_3
eras %>% 
  filter(month == 9) %>% 
  ggplot() +
  geom_line(
    aes(x = as.factor(ERAS), 
        y = num_candidate, 
        group = edu_status, 
        color = edu_status), 
    lwd = 1.2) + 
  geom_point(
    aes(x = as.factor(ERAS), 
        y = num_candidate, 
        color = edu_status), 
    size = 2) +
  theme_minimal(base_size = 14, base_family = "Roboto") +
  scale_color_brewer(palette = "Set1") +
  xlab("") +
  ylab("No. of Candidates") +
  geom_text(
    data = subset(eras, ERAS == 2018 & month == 9), 
    aes(
      x = as.factor(ERAS), 
      y = num_candidate, 
      color = edu_status, 
      label = Label
    ), 
    size = 4, 
    hjust = 1.1, 
    family = "Roboto"
  ) +
  geom_text(
    data = subset(eras, ERAS == 2019 & month == 9),
    aes(
      x = as.factor(ERAS),
      y = num_candidate, 
      color = edu_status,
      label = Label),
    size = 4, 
    hjust = -.15, 
    family = "Roboto"
  ) +
  theme(
    legend.position = "none", 
    axis.text = element_text(family = "Roboto"),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(family = "Roboto Medium", hjust = 0.5)
  ) +
  labs(
    title = "September Candidates by Educational Status \nAY 2018 and AY 2019", 
    caption = "Source: ERAS, 2014\u20132018") 

   
```


# Year over Year---Candidates 
 
```{r Figure 7, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  
# Candidates YOY
eras_hist %>% 
  filter(
    month, between(month, 7, 9)
  ) %>% 
  group_by(`ERAS Year`) %>% 
  summarise(
    Tot_Candidates = sum(`# of Applicants`)
  ) %>% 
  mutate(
    lagged = lag(Tot_Candidates)
  ) %>% 
  mutate(
    Pct_Change = ((Tot_Candidates - lagged) / lagged), 
    Bar_Cols = if_else(Pct_Change > 0, "Up", "Down")
  ) %>% 
  filter(`ERAS Year` != 2014) %>% 
  ggplot(
    aes(x = `ERAS Year`, y = Pct_Change, fill = Bar_Cols)
  ) +
  geom_bar(stat = "identity", width = .5) +
  scale_fill_manual(values = c("Up" = "#4267b1", "Down" = "#cccccc")) + 
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    legend.position = "none"
  ) +
  geom_text(
    aes(
      label = scales::percent(Pct_Change), 
      y = (Pct_Change + 0.007 * sign(Pct_Change))),
    family = "Roboto"
  ) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Percent Change Year over Year\u2014Candidates \nJuly\u2013September", 
       caption = "Source: ERAS, 2014\u20132018",
       y = "% Change Candidates")

```

# Year over Year---Applications
 
```{r Figure 8, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}

## Applications YOY
eras_hist %>% 
  filter(
    month, between(month, 7, 9)
  ) %>% 
  group_by(`ERAS Year`) %>% 
  summarise(
    Tot_Candidates = sum(`# of Applications`)
  ) %>% 
  mutate(
    lagged = lag(Tot_Candidates)
  ) %>% 
  mutate(
    Pct_Change = ((Tot_Candidates - lagged) / lagged), 
    Bar_Cols = if_else(Pct_Change > 0, "Up", "Down")
  ) %>% 
  filter(`ERAS Year` != 2014) %>% 
  ggplot(
    aes(x = `ERAS Year`, y = Pct_Change, fill = Bar_Cols)
  ) +
  geom_bar(stat = "identity", width = .5) +
  scale_fill_manual(values = c("Up" = "#4267b1", "Down" = "#cccccc")) + 
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    legend.position = "none"
  ) +
  geom_text(
    aes(
      label = scales::percent(Pct_Change), 
      y = (Pct_Change + 0.007 * sign(Pct_Change))),
    family = "Roboto"
  ) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Percent Change Year over Year\u2014Applications \nJuly\u2013September", 
       caption = "Source: ERAS, 2014\u20132018",
       y = "% Change Applications")


```

# Year over Year---Cumulative Candidates 
 
```{r Figure 9, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}

## Cumulative candidates 

eras_hist %>% 
  filter(
    month, 
    between(month, 7, 11)
  ) %>% 
  group_by(`ERAS Year`) %>% 
  mutate(Run_Tot = cumsum(`# of Applicants`)) %>% 
  ungroup() %>% 
  ggplot(aes(x = month, y = Run_Tot)) +
  geom_line(
    aes(color = factor(`ERAS Year`)), 
    lwd = 1.2) + 
  scale_color_manual(
    values = c("2014" = "#cccccc", "2015" = "#cccccc", "2016" =  "#cccccc",
               "2017" = "#cccccc", "2018" = "#cccccc","2019" = "#cc3466")
  ) +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(
      hjust =0.5, 
      family = "Roboto Medium"),
    legend.position = "none"
  ) + 
  labs(
    title = "Year over Year Cumulative Candidates \nAY 2014\u2013AY 2019", 
    y = "Total Cumulative Candidates", 
    caption = "Source: ERAS, 2014\u20132018",
    x = ""
  ) +
  ylim(225, 550) +
  annotate("text", 
           x = 9, 
           y = 410, 
           label = "AY 2019", 
           family = "Roboto", 
           color = "#010101"
  ) +
  scale_x_continuous(labels = month.name[7:11])


  
```


# Educational Status

```{r Figure 10, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300 }
  
## July-September
eras_july_sept <- eras %>%
  filter(month, between(month, 7, 9)) %>% 
  group_by(ERAS, edu_status) %>% 
  summarise(Tot_Cand = sum(num_candidate)) %>% 
  mutate(
    Label = paste0(edu_status, " ", as.character(Tot_Cand))
  ) 

eras_july_sept %>% 
  ggplot() +
  geom_line(
    aes(x = as.factor(ERAS), 
        y = Tot_Cand, 
        group = edu_status, 
        color = edu_status), 
    lwd = 1.2) + 
  geom_point(
    aes(x = as.factor(ERAS), 
        y = Tot_Cand, 
        color = edu_status), 
    size = 2) +
  theme_minimal(base_size = 14, base_family = "Roboto") +
  scale_color_brewer(palette = "Set1") +
  xlab("") +
  ylab("No. of Candidates") +
  geom_text_repel(
    data = subset(eras_july_sept, ERAS == 2018), 
    aes(
      x = as.factor(ERAS), 
      y = Tot_Cand, 
      color = edu_status, 
      label = Label
    ), 
    size = 4, 
    hjust = 1.1, 
    family = "Roboto",
    segment.alpha = 0,
  ) +
  geom_text_repel(
    data = subset(eras_july_sept, ERAS == 2019),
    aes(
      x = as.factor(ERAS),
      y = Tot_Cand, 
      color = edu_status,
      label = Label),
    size = 4, 
    hjust = -.15, 
    family = "Roboto", 
    segment.alpha = 0
  ) +
  theme(
    legend.position = "none", 
    axis.text = element_text(family = "Roboto"),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(family = "Roboto Medium", hjust = 0.5)
  ) +
  labs(
    title = "Cumulative Candidates by Educational Status \nAY 2018 and 2019", 
    caption = "Source: ERAS, 2014\u20132018") 

   
```


# Up Next

The next _Data Brief_ will report preliminary nephrology Match results on 
*Match Day, Wednesday, November 28*. 

_**Questions? Comments?**_ 

Contact ASN Data Science Officer Kurtis Pivert
at 202-699-0238 or [kpivert@asn-online.org](mailto:kpivert@asn-online.org).