---
title: "AY 2019 Nephrology Match---Preliminary Results"
author: "Kurtis Pivert"
date: ""
output: word_document
---

```{r setup, include=FALSE}

require(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
require(extrafont)
require(rmarkdown)
loadfonts(quiet = TRUE)
require(ggrepel)
require(RColorBrewer)
require(gt)
require(tidyverse)
  
```


```{r Match Data, include=FALSE}

## Match Data for Table with Sparklines

match <- read_excel(
  path = here::here("01_data",
                    "2018-11-28_AY-2019_Match-Results_Table.xlsx"),
  sheet = 3,
  col_names = TRUE)


tidymatch <- match %>%
  gather(key = "Year", value = "Value", `AY-2009`:`AY-2019`)



## Match Data for Visualizations

match2 <- read_excel(
  path = here::here("01_data",
                    "2018-11-28_AY-2019_Match-Results_Table.xlsx"),
  sheet = 4,
  col_names = TRUE)

## ERAS Data

## Edu Status

eras <- read_excel(
  here::here("01_data",
             "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"),
  sheet = "By Edu Status")

eras <- eras %>% 
  mutate(month = lubridate::month(month_year))
  
## Historical Totals

eras_hist <- read_excel(
  path = here::here("01_data", 
                    "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"),
  sheet = "Historical Totals",
  col_names = TRUE)

eras_hist <- eras_hist %>% 
  mutate(month = lubridate::month(`Month/Year`))
  

## NRMP/ACMGE/ASN Nephrology GME Data
gme <- read_excel(
  path = here::here("01_data",
                    "2017-04-26_ACGME-ASN-GME-NRMP_Total-Filled.xlsx")
  ) 

## Subset Data
gme <- gme %>% 
  select(year:acgmeFirstYear) %>% 
  filter(year <= 2016) %>% 
  rbind(
    c(2017, 284, 412), 
    c(2018, 285, 404)
    ) %>% 
  mutate(acgmeFirstYear = as.numeric(acgmeFirstYear))

```


## **ASN _Data Brief_** November 28, 2018
### [**Kurtis Pivert** *ASN Data Science Officer*](mailto:kpivert@asn-online.org)

### Contents
### I. Moving in Two Directions
### II. ERAS Application Data: A Look at the Candidates
### III. The Match in Context 

## I. Moving in Two Directions

_**Key Points**_ 


```{r Load Data, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}

  ## Edu Status
  eras <- read_excel(here::here("01_data", 
                                "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"), 
                     sheet = "By Edu Status")

  eras <- eras %>% mutate(month = lubridate::month(month_year))
  
  ## Historical Totals
  eras_hist <- read_excel(here::here("01_data", 
                                     "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"), 
                          sheet = "Historical Totals")

  eras_hist <- eras_hist %>% mutate(month = lubridate::month(`Month/Year`))
  
  
```


# AY 2019---Turning of the Tide?

July application data provided by [ERAS](https://www.aamc.org/data/facts/eras/) 
for the appointment year (AY) 2019 nephrology Match show an uptick in
total candidates and applications over the same time point in previous
recruitment cycles.  

### Total candidates in July are up ...

Candidate numbers in July have inched up over the past 3 application cycles. 
AY 2019 candidate totals for July (286) are 6% shy of AY 2014. (In 2014, 
available nephrology fellowship positions outnumbered candidates for 
the first time since the specialty rejoined the Match.) 


```{r Figure 1, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  eras_colors <- c("2014" = "#cccccc", "2015" = "#cccccc",  "2016" = "#cccccc", 
                    "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#3366cc")
  
  eras_hist %>% filter(month == 7) %>% 
    ggplot(aes(x = `ERAS Year`, y = `# of Applicants`)) +
    #geom_line(color = "#cc3366", lwd = 1.5) +
    geom_bar(stat = "identity", fill = c("#cccccc", "#cccccc", "#cccccc", 
                                         "#cccccc", "#cccccc","#3366cc"),
             width = .7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
    ylab("No. of Candidates") +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    ggtitle("Total Nephrology Candidates in July by ERAS Year")
  
```


##### _**Source**:_ ERAS, 2014--2018. 

### ... and candidate trends are reversing.

Starting with last year's application cycle, the year-over-year trend of declining 
candidates in July is slowly reversing, building on last year's increase. 



```{r Figure 2, echo=FALSE,  message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  eras_hist %>% filter(month == 7) %>% mutate(lagged = lag(`# of Applicants`)) %>% 
    mutate(Pct_Change = ((`# of Applicants` - lagged) / lagged)) %>% 
    filter(`ERAS Year` != 2014) %>% 
    ggplot(aes(x = `ERAS Year`, y = Pct_Change, fill = sign(Pct_Change))) +
    geom_bar(stat = "identity", width = .7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
  labs(y = "% Change Candidates",
      x = "ERAS Year") +
    theme(legend.position = "none") +
    geom_text(aes(label = scales::percent(Pct_Change), 
                  y = (Pct_Change + 0.007 * sign(Pct_Change))), family = "Roboto") +
    scale_y_continuous(labels = scales::percent) +
    ggtitle("Percent Change Year over Year\u2014Candidates in July")
   
```

##### _**Source**:_ ERAS, 2014--2018.

### Applications to nephrology fellowships are up slightly ...   

Total applications in July have rebounded from an apparent nadir in 2017. 

```{r Figure 3, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  eras_hist %>% filter(month == 7) %>% 
    ggplot(aes(x = `ERAS Year`, y = `# of Applications`)) +
    geom_bar(stat = 'identity', fill = c("#cccccc", "#cccccc", "#cccccc", 
                                         "#cccccc", "#cccccc","#3366cc"),
             width = 0.7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    labs(
      y = "No. of Applications",
      x = "ERAS Year") +
    ggtitle("Total Nephrology Applications in July by ERAS Year")

  
```

##### _**Source**:_ ERAS, 2014--2018.

### ... and growing slowly year over year.

The year over year percentages illustrate the stark decline in total nephrology 
applications experienced after the inversion in AY 2014.


```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=7, dpi= 300}
  eras_hist %>% filter(month == 7) %>% mutate(lagged = lag(`# of Applications`)) %>% 
    mutate(Pct_Change = ((`# of Applications` - lagged) / lagged)) %>% 
    filter(`ERAS Year` != 2014) %>% 
    ggplot(aes(x = `ERAS Year`, y = Pct_Change, fill = sign(Pct_Change))) +
    geom_bar(stat = "identity", width = .7) +
    theme_minimal(base_size = 14, base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(family = "Roboto Medium", hjust = 0.5),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3")) +
    ylab("% Change Applications") +
    theme(legend.position = "none") +
    geom_text(aes(label = scales::percent(Pct_Change), 
                  y = (Pct_Change + 0.007 * sign(Pct_Change))), family = "Roboto") +
    scale_y_continuous(labels = scales::percent) +
    ggtitle(label = "Percent Change Year over Year\u2014Applications in July")
   
```

##### _**Source**:_ ERAS, 2014--2018.

### IMG candidates are back ...

July numbers show a strong rebound in international medical graduate (IMG) candidates
applying to the specialty. While US IMGs and DOs continue to edge up, US MDs declined 
in July by 6%. 


```{r Figure 5, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  
        eras <-  eras %>% mutate(Label = paste0(edu_status, " ", 
                                                as.character(num_candidate)))  
        
        eras %>% filter(month == 7) %>% ggplot() +
          geom_line(aes(x = as.factor(ERAS), y = num_candidate, group = edu_status, 
                                      color = edu_status), lwd = 1.2) + 
          geom_point(aes(x = as.factor(ERAS), y = num_candidate, color = edu_status), 
                     size = 2) +
          theme_minimal(base_size = 14, base_family = "Roboto") +
          scale_color_brewer(palette = "Set1") +
          xlab("") +
          ylab("No. of Candidates") +
          geom_text(data = subset(eras, ERAS == 2018 & month == 7), 
                    aes(x = as.factor(ERAS), y = num_candidate, color = edu_status, 
                        label = Label), 
                          size = 4, hjust = 1.1, family = "Roboto") +
          geom_text(data = subset(eras, ERAS == 2019 & month == 7), 
                    aes(x = as.factor(ERAS), y = num_candidate, color = edu_status, 
                        label = Label), 
                          size = 4, hjust = -.15, family = "Roboto")+
          theme(legend.position = "none", axis.text = element_text(family = "Roboto"),
                panel.background = element_rect(fill = "#fffff3", 
                                                color = "#fffff3"),
                plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
                plot.title = element_text(family = "Roboto Medium", hjust = 0.5)) +
          ggtitle(label = "July AY 2019 Candidates by Educational Status") 
          
        
        
```


##### _**Source**:_ ERAS, 2014--2018.

### ...but total candidates ...   

Although its early in the application cycle, it's possible the total candidates 
for the AY 2019 application cycle may match that of AY 2018.  


```{r Figure 6, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  eras_colors <- c("2014" = "#cccccc", "2015" = "#cccccc",  "2016" = "#cccccc", 
                    "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#3366cc") 
  
  Avg <- eras_hist %>% filter(!`ERAS Year` == 2019) %>% group_by(`ERAS Year`) %>% 
  summarize(Total = sum(`# of Applicants`)) %>% summarize(Avg = mean(Total))
               

  eras_hist %>% group_by(`ERAS Year`) %>% 
    summarise(Total = sum(`# of Applicants`)) %>% 
    ggplot(aes(x = `ERAS Year`, y = Total)) +
    geom_bar(stat = "identity", fill = c("#cccccc", "#cccccc", "#cccccc", 
                                         "#cccccc", "#cccccc","#3366cc"),
             width = 0.7) +
    theme_minimal(base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust =0.5, family = "Roboto Medium")) +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    #geom_hline(aes(yintercept = mean(Total))) + 
    geom_hline(aes(yintercept = Avg$Avg)) + 
    theme(legend.position = "none") +
    geom_text(aes(label = "Mean Total Candidates", x = 2018.5, y = 500),
              family = "Roboto", color = "#3366cc") +
    ylab("Total Candidates per Application Cycle") +
    ggtitle("Total Candidates by ERAS Year (AY 2019 = July Only)")
 

```

##### _**Source**:_ ERAS, 2014--2018.

### ...and applications are still down compared to historic averages. 

Despite the upturn in candidates, it's unknown when or if total applications will ever return to former levels, indicating a continued lack of selectivity.  


```{r Figure 7, echo=FALSE,  message=FALSE, warning=FALSE, cache=TRUE, fig.width=6, dpi= 300}

  eras_colors <- c("2014" = "#cccccc", "2015" = "#cccccc",  "2016" = "#cccccc", 
                    "2017" = "#cccccc",  "2018" = "#cccccc","2019" = "#3366cc") 
                 
  Avg_Apps <- eras_hist %>% filter(!`ERAS Year` == 2019) %>% group_by(`ERAS Year`) %>% 
  summarize(Total = sum(`# of Applications`)) %>% summarize(Avg = mean(Total))                   

  eras_hist %>% group_by(`ERAS Year`) %>% 
    summarise(Total = sum(`# of Applications`)) %>% 
    ggplot(aes(x = `ERAS Year`, y = Total)) +
    geom_bar(stat = "identity", 
             fill = c("#cccccc", "#cccccc", "#cccccc", "#cccccc", "#cccccc",
                                 "#3366cc"),
             width = 0.7) +
    theme_minimal(base_family = "Roboto") +
    theme(panel.grid.minor = element_blank(),
           panel.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
          plot.title = element_text(hjust = 0.5, family = "Roboto Medium")) +
    scale_x_continuous(breaks = 2014:2019, labels = as.character(2014:2019)) +
    geom_hline(aes(yintercept = Avg_Apps$Avg)) + 
    theme(legend.position = "none") +
    geom_text(aes(label = "Mean Total Applications", x = 2018.5, y = 9900),
              family = "Roboto", color = "#3366cc") +
    ylab("Total Applications per Application Cycle") +
    ggtitle("Total Applications by ERAS Year (AY 2019 = July Only)")
 

```

##### _**Source**:_ ERAS, 2014--2018.

### Up Next

Future _Data Briefs_ will report ERAS application data as it becomes available. 

_**Questions? Comments?**_ 

Contact ASN Data Science Officer Kurtis Pivert
at 202-699-0238 or [kpivert@asn-online.org](mailto:kpivert@asn-online.org).

