---
title: "AY 2019 Nephrology Match---Preliminary Results"
author: "Kurtis Pivert, **ASN Data Science Officer**"
date: "November 2018"
output:
  powerpoint_presentation
---

```{r setup, include=FALSE}

require(knitr)
knitr::opts_chunk$set(echo = TRUE)
require(here)
library(readxl)
require(extrafont)
require(rmarkdown)
loadfonts(quiet = TRUE)
require(ggrepel)
require(pander)
require(RColorBrewer)
require(tidyverse)

```



```{r Match Data, include=FALSE}

## Match Data for Table with Sparklines

match <- read_excel(
  path = here::here("content_data/01_data",
                    "2018-11-28_AY-2019_Match-Results_Table.xlsx"),
  sheet = 3,
  col_names = TRUE)

## Match Data for Visualizations

match2 <- read_excel( 
  path = here::here("content_data/01_data",
                    "2018-11-28_AY-2019_Match-Results_Table.xlsx"),
  sheet = 4,
  col_names = TRUE)

## ERAS Data

## Edu Status

eras <- read_excel(
  here::here("content_data/01_data",
             "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"),
  sheet = "By Edu Status")

eras <- eras %>% 
  mutate(month = lubridate::month(month_year))
  
## Historical Totals

eras_hist <- read_excel(
  path = here::here("content_data/01_data", 
                    "2018-11-26_ERAS_Legacy-Data_AY-2014_AY-2019.xlsx"),
  sheet = "Historical Totals",
  col_names = TRUE)

eras_hist <- eras_hist %>% 
  mutate(month = lubridate::month(`Month/Year`))
  

## NRMP/ACMGE/ASN Nephrology GME Data
gme <- read_excel(
  path = here::here("content_data/01_data",
                    "2017-04-26_ACGME-ASN-GME-NRMP_Total-Filled.xlsx")
  ) 

## Subset Data
gme <- gme %>% 
  select(year:acgmeFirstYear) %>% 
  filter(year <= 2016) %>% 
  rbind(
    c(2017, 284, 412), 
    c(2018, 285, 404)
    ) %>% 
  mutate(acgmeFirstYear = as.numeric(acgmeFirstYear))

```

# I. Moving in Two Directions


# Unfilled training tracks...  


```{r Unfilled Tracks, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

cols_2019 <- c(rep("#cccccc", 10), "#3366cc")

match2 %>% 
  mutate(
    `Percent Unfilled Tracks`= round(
      `Unfilled Tracks` / `Offered Tracks`, 3) * 100) %>%  
  ggplot(
    aes(
      Year, 
      `Percent Unfilled Tracks`,
      fill = factor(Year))
    ) + 
  geom_bar(
    stat = "identity"
    ) +
  scale_fill_manual(values = cols_2019) +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
    ) +
  labs(
    y = "Percent Unfilled Tracks",
    x = "Appointment Year",
    title = paste(
      "Percentage Unfilled Nephrology Tracks: \n",
      "AY 2009 to AY 2019")
    ) +
  scale_x_continuous(
    breaks = 2009:2019, 
    labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016",
               "2017", "2018", "2019")
    ) +
  geom_text(
    aes(
      label = scales::percent(`Percent Unfilled Tracks` / 100), 
      x = Year, 
      y = `Percent Unfilled Tracks`),
    nudge_y = 5, 
    family= "Roboto", 
    show.legend = F,
    color = "black", 
    size = 4) +
  scale_y_continuous(
    breaks = seq(20, 100, 20),
    labels = paste0(seq(20, 100, 20), "%")) 


```


# ...and unfilled positions edged down in the AY 2019 Match.

```{r Unfilled Positions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

match2 %>% 
  mutate(
    `Percent Unfilled Positions`= round(
      `Unfilled Positions` / `Offered Positions`, 3) * 100) %>%  
  ggplot(
    aes(
      Year, 
      `Percent Unfilled Positions`,
      fill = factor(Year))
    ) + 
  geom_bar(
    stat = "identity"
    ) +
  scale_fill_manual(values = cols_2019) +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
    ) +
  labs(
    y = "Percent Unfilled Positions",
    x = "Appointment Year",
    title = paste(
      "Percentage Unfilled Nephrology Positions: \n",
      "AY 2009 to AY 2019")
    ) +
  scale_x_continuous(
    breaks = 2009:2019, 
    labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016",
               "2017", "2018", "2019")
    ) +
  geom_text(
    aes(
      label = scales::percent(`Percent Unfilled Positions` / 100), 
      x = Year, 
      y = `Percent Unfilled Positions`),
    nudge_y = 5, 
    family= "Roboto", 
    show.legend = F,
    color = "black", 
    size = 4) +
  scale_y_continuous(
    breaks = seq(20, 100, 20),
    labels = paste0(seq(20, 100, 20), "%")) 

```



# Yet the gap in offered and filled positions...


```{r Offered vs. Filled Positions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

match2 %>% 
  ggplot(
    aes(
      Year,
      `Offered Positions`
     )
    ) + 
  geom_freqpoly(
    stat = "identity",
    lwd = 1.2, 
    color = "#cc3466"
    ) + 
  geom_bar(
    data = match2, 
    mapping = aes(
      Year, 
      `Filled Positions`,
       fill = factor(Year)
      ), 
    stat = "identity") +
    scale_fill_manual(values = cols_2019) +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
    ) +
  labs(
    y = "Positions",
    x = "Appointment Year",
    title = paste(
      "Offered vs. Filled Nephrology Fellowship Positions: \n",
      "AY 2009 to AY 2019")
    ) +
  scale_x_continuous(
    breaks = 2009:2019, 
    labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016",
               "2017", "2018", "2019")
    ) +
  geom_text(
    aes(
      label = "Offered Positions", 
      x = 2014, 
      y = 445),
   # nudge_y = 5, 
    family= "Roboto", 
    show.legend = F,
    color = "#cc3466", 
    size = 4) +
  geom_text(
    aes(
      label = "Filled Positions", 
      x = 2017, 
      y = 350),
   # nudge_y = 5, 
    family= "Roboto", 
    show.legend = F,
    color = "#cccccc", 
    size = 4) 


```


# ... and training tracks, while narrowing, remains wide. 


```{r Offered vs. Filled Tracks, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

match2 %>% 
  ggplot(
    aes(
      Year,
      `Offered Tracks`
     )
    ) + 
  geom_freqpoly(
    stat = "identity",
    lwd = 1.2, 
    color = "#cc3466"
    ) + 
  geom_bar(
    data = match2, 
    mapping = aes(
      Year, 
      `Filled Tracks`,
       fill = factor(Year)
      ), 
    stat = "identity") +
    scale_fill_manual(values = cols_2019) +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
    ) +
  labs(
    y = "Tracks",
    x = "Appointment Year",
    title = paste(
      "Offered vs. Filled Nephrology Training Tracks: \n",
      "AY 2009 to AY 2019")
    ) +
  scale_x_continuous(
    breaks = 2009:2019, 
    labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016",
               "2017", "2018", "2019")
    ) +
  geom_text(
    aes(
      label = "Offered Tracks", 
      x = 2014, 
      y = 165),
   # nudge_y = 5, 
    family= "Roboto", 
    show.legend = F,
    color = "#cc3466", 
    size = 4) +
  geom_text(
    aes(
      label = "Filled Tracks", 
      x = 2016, 
      y = 85),
   # nudge_y = 5, 
    family= "Roboto", 
    show.legend = F,
    color = "#cccccc", 
    size = 4) 


```


# An increasing number of US-IMGs and DOs are entering nephrology...


```{r Matched Fellows by Educational Status, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

match2_Label <- match2 %>% 
  select(
    Year, `US MD Matched`, `DO Matched`, `US-IMG Matched`, `IMG Matched`
    ) %>% 
  gather(
    key = "EduStatus", 
    value = "Number", 
    `US MD Matched`:`IMG Matched`
    )
       
match2 %>% 
  select(
    Year, `US MD Matched`, `DO Matched`, `US-IMG Matched`, `IMG Matched`
    ) %>% 
  gather(
    key = "EduStatus", 
    value = "Number", 
    `US MD Matched`:`IMG Matched`
    ) %>% 
  ggplot(
    aes(
      x=Year, 
      y= Number, 
      color = EduStatus)
    ) +
  geom_line(lwd=1.2, lineend = "round") +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
    ) + 
  scale_color_manual(
    values = c("#9344bf",  "#cc3466", "#70bf44", "#3366cc")
    ) +
   # scale_color_manual(
  #   values = c("#000000", "#cccccc","#cc9933",
  #              "#3366cc","#66cc33","#cc3366"),
  #   guide= guide_legend(title = "Educational \n Status",
  #                       title.hjust = .5)
  #   ) +
  labs(title = "Matched Nephrology Fellows by Education Status \n AY 2009 to AY 2019",
       x = "Appointment Year",
       y = "Matched Fellows") +
  scale_x_continuous(
    breaks = seq(2009, 2019, 1),
    labels = as.character(seq(2009, 2019, 1))) +
   geom_text_repel(
    data = subset(
      match2_Label,
      Year == 2011
      ),
    aes(
      x = 2011, 
      y = Number, 
      color = EduStatus, 
      label = EduStatus),
    size = 3.5, 
    hjust = 1.1, 
    family = "Roboto",
    segment.alpha = 0
    ) 



```


# ...and nearly all candidates preferring the specialty obtained fellowships.



```{r Figure Percent Pref Neph Matched, echo=FALSE, fig.width=6, dpi= 300}

match2 %>%
  mutate(`Percent Applicants Matched` = round(
    `Applicants Prefer Nephrology Matched` / `Applicants Prefer Nephrology`, 3) * 100) %>% 
  ggplot(
       aes(
         Year, 
         `Percent Applicants Matched`)
       ) + 
  geom_line(
    colour ="#3366cc",
    lwd=2, 
    lineend = "round") +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank()
    ) +
  labs(
    y = "Percent Applicants Matched",
    x = "Appointment Year",
    title = paste(
      "Applicants Preferring Nephrology Matched: \n",
      "AY 2009 to AY 2019")
    ) + 
  ylim(40, 100) +
  scale_x_continuous(
    breaks = 2009:2019, 
    labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016",
               "2017", "2018", "2019")
    ) +
  geom_text(
    aes(
      label = scales::percent(`Percent Applicants Matched` / 100), 
      x = Year, 
      y = `Percent Applicants Matched`), 
    family= "Roboto", 
    show.legend = F, 
    color = "black", 
    vjust = -2, 
    size = 4) +
  expand_limits(
    y = 110
  )


```

# II. ERAS Application Data: A Look at the Candidates 

# Year over Year---Candidates 

```{r YOY Candidates, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}
  
# Candidates YOY
eras_hist %>% 
  filter(
    month, between(month, 7, 10)
  ) %>% 
  group_by(`ERAS Year`) %>% 
  summarise(
    Tot_Candidates = sum(`# of Applicants`)
  ) %>% 
  mutate(
    lagged = lag(Tot_Candidates)
  ) %>% 
  mutate(
    Pct_Change = ((Tot_Candidates - lagged) / lagged), 
    Bar_Cols = if_else(Pct_Change > 0, "Up", "Down")
  ) %>% 
  filter(`ERAS Year` != 2014) %>% 
  ggplot(
    aes(x = `ERAS Year`, y = Pct_Change, fill = Bar_Cols)
  ) +
  geom_bar(stat = "identity", width = .5) +
  scale_fill_manual(values = c("Up" = "#3366cc", "Down" = "#cccccc")) + 
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    legend.position = "none"
  ) +
  geom_text(
    aes(
      label = scales::percent(Pct_Change), 
      y = (Pct_Change + 0.007 * sign(Pct_Change))),
    family = "Roboto"
  ) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Percent Change Year over Year\u2014Candidates", 
       caption = "Source: ERAS, 2014\u20132018",
       y = "% Change Candidates",
       x = "ERAS Year")

```

# Year over Year---Applications


```{r YOY Applications, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}
## Applications YOY
eras_hist %>% 
  filter(
    month, between(month, 7, 10)
  ) %>% 
  group_by(`ERAS Year`) %>% 
  summarise(
    Tot_Candidates = sum(`# of Applications`)
  ) %>% 
  mutate(
    lagged = lag(Tot_Candidates)
  ) %>% 
  mutate(
    Pct_Change = ((Tot_Candidates - lagged) / lagged), 
    Bar_Cols = if_else(Pct_Change > 0, "Up", "Down")
  ) %>% 
  filter(`ERAS Year` != 2014) %>% 
  ggplot(
    aes(x = `ERAS Year`, y = Pct_Change, fill = Bar_Cols)
  ) +
  geom_bar(stat = "identity", width = .5) +
  scale_fill_manual(values = c("Up" = "#4267b1", "Down" = "#cccccc")) + 
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.background = element_rect(fill = "#fffff3", color = "#fffff3"), 
    plot.title = element_text(hjust = 0.5, family = "Roboto Medium"),
    plot.background = element_rect(fill = "#fffff3", color = "#fffff3"),
    legend.position = "none"
  ) +
  geom_text(
    aes(
      label = scales::percent(Pct_Change), 
      y = (Pct_Change + 0.007 * sign(Pct_Change))),
    family = "Roboto"
  ) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Percent Change Year over Year\u2014Applications", 
       caption = "Source: ERAS, 2014\u20132018",
       y = "% Change Applications",
       x = "ERAS Year")
```


# Year over Year---Cumulative Candidates 

```{r Figure 9, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

## Cumulative candidates 

eras_hist %>% 
  filter(
    month, 
    between(month, 7, 11)
  ) %>% 
  group_by(`ERAS Year`) %>% 
  mutate(Run_Tot = cumsum(`# of Applicants`)) %>% 
  ungroup() %>% 
  ggplot(aes(x = month, y = Run_Tot)) +
  geom_line(
    aes(color = factor(`ERAS Year`)), 
    lwd = 1.2) + 
  scale_color_manual(
    values = c("2014" = "#cccccc", "2015" = "#cccccc", "2016" =  "#cccccc",
               "2017" = "#cccccc", "2018" = "#cccccc","2019" = "#cc3466")
  ) +
  theme_minimal(
    base_size = 14,
    base_family = "Roboto") +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(
      hjust =0.5, 
      family = "Roboto Medium"),
    legend.position = "none"
  ) + 
  labs(
    title = "Year over Year Cumulative Candidates \nAY 2014\u2013AY 2019", 
    y = "Total Cumulative Candidates", 
    caption = "Source: ERAS, 2014\u20132018",
    x = ""
  ) +
  ylim(225, 550) +
  annotate("text", 
           x = 9, 
           y = 420, 
           label = "AY 2019", 
           family = "Roboto", 
           color = "#010101"
  ) +
  scale_x_continuous(labels = month.name[7:11])


  
```



# Fellow Educational Status

```{r slopegraph, echo=FALSE, fig.width=6, dpi= 300}

eras_slope <- eras %>% 
  filter(
    ERAS %in% c(2018, 2019)
    ) %>% 
  filter(
    between(month, 7, 10)
    ) %>% 
  group_by(
    ERAS, 
    edu_status
    ) %>% 
  summarize(
    Totals = sum(num_candidate)
    ) %>% 
  mutate(
    Label = paste0(
      edu_status, 
      " ",
      as.character(Totals))
    ) 
  
eras %>% 
  filter(
    ERAS %in% c(2018, 2019)
    ) %>% 
  filter(
    between(month, 7, 10)
    ) %>% 
  group_by(
    ERAS, 
    edu_status
    ) %>% 
  summarize(
    Totals = sum(num_candidate)
    ) %>% 
  mutate(
    Label = paste0(
      edu_status, 
      " ",
      as.character(Totals))
    ) %>% 
  ggplot() +
  geom_line(
    aes(x = as.factor(ERAS), 
        y = Totals, 
        group = edu_status, 
        color = edu_status), 
    lwd = 1.2
    ) + 
  geom_point(
    aes(x = as.factor(ERAS), 
        y = Totals, 
        color = edu_status),
    size = 2
    ) +
  theme_minimal(
    base_size = 14, 
    base_family = "Roboto"
    ) +
  scale_color_manual(
    values = c( "#cc3466", "#9344bf", "#70bf44", "#3366cc")
    ) +
  # scale_color_brewer(
  #   palette = "Set1"
  #   ) + 
  labs(
    x = "", 
    y = "No. of Candidates",
    title = "Candidates by Educational Status\n AY 2018 and AY 2019"
    ) +
  geom_text_repel(
    data = subset(
      eras_slope, 
      ERAS == 2018
      ), 
    aes(
      x = as.factor(ERAS), 
      y = Totals, 
      color = edu_status, 
      label = Label),
    size = 4, 
    hjust = 1.1, 
    family = "Roboto",
    segment.alpha = 0) +
  geom_text_repel(
    data = subset(
      eras_slope, 
      ERAS == 2019
      ), 
    aes(
      x = as.factor(ERAS), 
      y = Totals, 
      color = edu_status, 
      label = Label),
    size = 4, 
    hjust = -.15, 
    family = "Roboto",
    segment.alpha = 0) +
  theme(
    legend.position = "none", 
    axis.text = element_text(family = "Roboto"),
    panel.background = element_rect(
      fill = "#fffff3",
      color = "#fffff3"),
    plot.background = element_rect(
      fill = "#fffff3", 
      color = "#fffff3"),
    plot.title = element_text(family = "Roboto Medium", hjust = 0.5)) +
  ylim(20, 200)

```


# III. The Match in Context 


```{r Nephrology GME Census, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, dpi= 300}

ggplot(
  gme,
  aes(
    x = year
  )
) +
  geom_line(
    aes(
      y = gme$nrmpFilled
    ),
    colour = "#cc3366",
    lwd = 1.2
  ) +
  geom_line(aes(y = gme$acgmeFirstYear),
    colour = "#3366cc",
    lwd = 1.2
  ) +
  geom_ribbon(aes(
    ymin = gme$nrmpFilled,
    ymax = gme$acgmeFirstYear
  ), alpha = 0.2) +
  theme_minimal(base_family = "Roboto", base_size = 14) +
  xlab(label = "Year") +
  ylab(label = "No. of Filled Positions") +
  scale_x_continuous(
    breaks = 2009:2018, labels =
      as.character(2009:2018)
  ) +
  ylim(200, 500) +
  scale_y_continuous(
    breaks = seq(200, 500, 50), labels =
      as.character(seq(200, 500, 50))
  ) +
  ggtitle(label = "1st-Year Fellows in the\n Nephrology Match Era") +
  theme(plot.title = element_text(hjust = 0.5, size = 16, family = "Roboto Black")) +
  geom_text(aes(x = 2010.5, y = 487),
    label = "1st-Year Fellows in Training \nACGME/ASN",
    family = "Roboto", colour = "#3366cc", size = 4
  ) +
  geom_text(aes(x = 2011, y = 330),
    label = "1st-Year Fellows Matched",
    family = "Roboto", colour = "#cc3366", size = 4
  ) +
  geom_segment(aes(x = 2018, xend = 2018, y = 285, yend = 404), lwd = 1.2) +
  # geom_segment(aes(x = 2018, xend = 2018, y = 375, yend = 404), lwd = 1.2) +
  geom_text(aes(x = 2016.75, y = 365),
    label = "2018 Difference\n128 Fellows",
    family = "Roboto", colour = "black", size = 4
  ) +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(
      fill = "#fffff3",
      color = "#fffff3"
    ),
    plot.background = element_rect(
      fill = "#fffff3",
      color = "#fffff3"
    )
  ) +
  expand_limits(y = c(200, 500)) ## NICE!

```


# _**Questions? Comments?**_ 

Contact ASN Data Science Officer Kurtis Pivert
at 202-699-0238 or [kpivert@asn-online.org](mailto:kpivert@asn-online.org).