---
title: "Nephrology Key Contributor to Hospital Revenue"
author: "Kurtis Pivert, ASN Data Science Officer"
date: ""
output: 
  word_document:
    reference_docx: template.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r 00_Load Packages, message=FALSE, warning=FALSE, echo=FALSE}

require(knitr)
require(extrafont)
loadfonts(quiet = TRUE)
require(tidyverse)

```

```{r 01_Load_Data, message=FALSE, warning=FALSE, echo=FALSE}

mh <- tbl_df(
  read.table(
    header = TRUE, 
    text = "
Specialty Average_Revenue Average_Salary
Cardiology_(Invasive) $3,484,375 $590,000
Cardiology/Non-Inv. $2,310,000 $427,000
Cardiovascular_Surgery $3,697,916 $425,000
Family_Practice $2,111,931 $241,000
Gastroenterology $2,965,277 $487,000
General_Surgery $2,707,317 $350,000
Hematology/Oncology $2,855,000 $425,000
Internal_Medicine $2,675,387 $261,000
Nephrology $1,789,062 $272,000
Neurology $2,052,884 $301,000
Neurosurgery $3,437,500 $687,000
OB/GYN $2,024,193 $324,000
Ophthalmology $1,440,217 $300,000
Orthopedic_Surgery $3,286,764 $533,000
Otolaryngology $1,937,500 $405,000
Pediatrics $1,612,500 $230,000
Psychiatry $1,820,512 $261,000
Pulmonology $2,361,111 $418,000
Urology $2,161,458 $386,000
",
    stringsAsFactors = FALSE)
) 

df <- read_csv(
  file = here::here("03_reports", "06_MH-Revenue-Shiny/MH-Revenue/table.csv")
)


# * Clean and Mutate ------------------------------------------------------


mh <- mh %>% 
  mutate(
    `Mean Revenue` = parse_number(Average_Revenue),
    `Mean Salary` = parse_number(Average_Salary)
  ) %>% 
  mutate(
    ROI = (`Mean Revenue` - `Mean Salary`) / `Mean Salary` 
  ) %>% 
  arrange(
    desc(ROI), 
    `Mean Salary`
  ) %>%
  select(
    Specialty,
    `Mean Revenue`,
    `Mean Salary`,
    ROI
  )



```



## ASN _Data Brief_---Nephrology Key Contributor to Hospital Revenue 


Newly released survey data collected from 62 hospital CFOs found nephrology makes 
key contributions to hospital systems gross revenue. The report from 
[Merrit Hawkins](https://www.merritthawkins.com/news-and-insights/blog/healthcare-news-and-trends/New-Survey-Shows-Physicians-Are-Key-Revenue-Generators-for-Hospitals/)
also found the ratio of return on investment (ROI) for nephrologists' median salary
was higher than gastroenterology, cardiology, and pulmonology. 


## Ranking of Specialities by ROI

```{r 01_Table, warning=FALSE, echo=FALSE, message=FALSE}

mh %>% 
  mutate(
    `Mean Revenue` = scales::dollar(`Mean Revenue`),
    `Mean Salary` = scales::dollar(`Mean Salary`),
    ROI = round(ROI, 2)
    ) %>% 
      kable()

```


